---
title: "My hometown"
author: "Agustin González-Quel"
date: "04 de mayo de 2017"
output: html_document
---

# This is my Hometown

Dated May the 5th, 2017

## Linares
I was born in Linares (Andalucia - Spain). It is a place of about 60.000 inhabitants located in the north-east of Andalucia. A funny hot town in summer; not very cold in winter. I spent there my first 17 years of life. 


```{r setup, echo = FALSE}
library(leaflet)

LinaresIcon <- makeIcon(iconUrl = "https://upload.wikimedia.org/wikipedia/commons/3/38/Escudo_de_Linares.svg",
                        iconWidth = 51*215/230, iconHeight = 51,
                        iconAnchorX = 31*215/230/2, iconAnchorY = 16)

Linares_map <- leaflet()
Linares_map <- addTiles(Linares_map)
Linares_map <- addMarkers(Linares_map, 
                          lat = 38.09456210527424, 
                          lng = -3.6322420835494995, 
                          icon = LinaresIcon,
                          popup = "Linares")
Linares_map
```

And now, Linares located in Andalucia, the size of the circles represents the size of the city.

```{r echo = FALSE}
cities <- data.frame(name = c("Sevilla", "Granada", "Córdoba", "Jaen", "Málaga", "Cádiz",
                               "Linares"),
                     pop = c(690000, 235000, 327000, 115000, 569000, 119000, 59000),
                     lat = c(37.38161597475995, 37.17618429254936, 37.88731847929118,
                             37.76847577247014, 36.714118564660595, 36.52950186333476,
                             38.09456210527424),
                     lng = c(-5.9882354736328125, -3.5932159423828125, -4.7728729248046875,
                             -3.7878799438476562, -4.426116943359375, -6.29791259765625,
                             -3.6322420835494995))

cities %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircles(weight = 1, radius = sqrt(cities$pop) *30)
```

 


###Credits
The Linares Simbol is licensed under the Creative Commons Attribution-Share Alike 4.0 International (https://creativecommons.org/licenses/by-sa/4.0/) By user:SanchoPanzaXXI (Own work) [GFDL (http://www.gnu.org/copyleft/fdl.html) or CC BY-SA 4.0-3.0-2.5-2.0-1.0 (http://creativecommons.org/licenses/by-sa/4.0-3.0-2.5-2.0-1.0)], via Wikimedia Commons.
